timesliced_random_cell_selection

### 2018-10-30 src/timesliced_random_cell_selection.Rmd
all of the random! timesliced!

Note that the file are saved in /src. Manually move them to output/bio/background

```{r}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(timeslice)
  time_cell <- unique_cell_xyz
  time_cell <- time_cell[!time_cell$id_depth %in% timeslice$id_depth, , drop = FALSE]
  write.csv(time_cell, paste0(names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

@@

```{r}
bckrnd_folder <- "../output/bio/background/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder

# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  assign(bckrnd_list[i], 
  read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  )
  #now do something....

  }

```
and that something you are going to do is randomly select rows....

manual attempt:
```{r}
library(dplyr)
test_cell_selection <- read.csv("../output/bio/background/1998.10.csv", header = TRUE) #just load one csv to play with
test_ran_cell_sel <- sample_n(test_cell_selection, 10) #where 10 = number of rows to sample
```

>>>>

```{r timesliced unique unsampled}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
bckoutput <- "../output/bio/background/raw/" #where the files are to be saved to
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(timeslice)
  time_cell <- unique_cell_xyz
  time_cell <- time_cell[!time_cell$id_depth %in% timeslice$id_depth, , drop = FALSE]
  write.csv(time_cell, paste0(bckoutput, names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

@@

```{r}
library(dplyr)
bckrnd_folder <- "../output/bio/background/raw/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  test_sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  test_sel <- sample_n(test_sel, 10000) #where 10000 = number of rows to sample (large sample as per maxent)
  write.csv(test_sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}

```

ok now i have a ton of files for random background points broken into timeslices. I'd like to add a colum for year and one for month to each of these datasets. They should be populated based on the name of the file (e.g. 1998.4.csv would have year = 1998 and month = 4)

```{r}

```
